Recurrent Neural Networks

### 2017-12-11 paper/paper.tex
Fixes seq2seq model

	In this practice we explore the effects of the different elements of RNNs using a specific dataset\footnote{https://upc-mai-dl.github.io/rnn-lab-autonomous/}. In this case we extend the Wind prediction example that we used in the previous guided session.

@@

	The code related to this work is public and available at github\footnote{https://github.com/juanlao7/DL-lab2}.

@@

	\begin{itemize}
		\item \emph{As expected}, models that try to predict more steps forward lead to lower accuracies.
		\item \emph{As expected}, this sequence-to-sequence model has a lower error than the previous multi step approach. The previous model, with a window size of 6 and 24 unknown inputs, has a MSE of 1.06895 while this model has a MSE of 0.384457 when predicting 24 steps.
	\end{itemize}

>>>>

	In this practice we explore the effects of the different elements of RNNs using a specific dataset\footnote{\url{https://upc-mai-dl.github.io/rnn-lab-autonomous/}}. In this case we extend the Wind prediction example that we used in the previous guided session.

@@

	The code related to this work is public and available at github\footnote{\url{https://github.com/juanlao7/DL-lab2}}.

@@

	\begin{itemize}
		\item \emph{As expected}, models that try to predict more steps forward lead to lower accuracies.
		\item \emph{As expected}, this sequence-to-sequence model has a lower error than the previous multi step approach. The previous model, with a window size of 6 and 24 unknown inputs, has a MSE of 1.06895 while this model has a MSE of 0.368767 when predicting 24 steps.
	\end{itemize}
